Deploy

### 2021-05-26 README.Rmd
Complete deploy
finalize naming

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
<!-- badges: end -->

@@

Please refer to the [overview](overview_gh.md) for an introduction to this package. If you use BTM, please refer to the [BTM Vignette](btm_gh.md).

@@

Chan et al., (2020). oolong: An R package for validating  automated content analysis tools. Journal of Open Source Software, 5(55), 2461, [https://doi.org/10.21105/joss.02461](https://doi.org/10.21105/joss.02461)

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
[![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
<!-- badges: end -->

@@

Please refer to the [overview](overview_gh.md) for an introduction to this package. If you need to deeploy the test online, please refer to the [Deployment Vignette](deploy_gh.md). If you use BTM, please refer to the [BTM Vignette](btm_gh.md).

@@

Chan C-h. & Sältzer M., (2020). oolong: An R package for validating  automated content analysis tools. Journal of Open Source Software, 5(55), 2461, [https://doi.org/10.21105/joss.02461](https://doi.org/10.21105/joss.02461)

### 2021-05-26 vig_body.Rmd
fix a bug of ti when input_corpus is NULL, ref #49
finalize naming

```{r, include = FALSE}
### Mock this process
oolong_test$.__enclos_env__$private$test_content$word$answer <- oolong_test$.__enclos_env__$private$test_content$word$intruder
oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
```

@@

```{r, include = FALSE}
genius_topic <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
    return(obj1)
}
genius_word <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
    return(obj1)
}
oolong_test <- genius_word(genius_topic(oolong_test))
oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
oolong_test$lock()
```

@@

```{r warplda2}
### Just word intrusion test.
oolong_test <- ti(abstracts_warplda, userid = "Lionel")
oolong_test
```

@@

```{r, include = FALSE}
oolong_test$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
))
```

@@

```{r, include = FALSE}
trump$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))

trump2$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(5L, 3L, 2L, 5L, 3L, 1L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))
trump$lock()
trump2$lock()
```

>>>>

```{r, include = FALSE}
### Mock this process
oolong_test$.__enclos_env__$private$test_content$wi$answer <- oolong_test$.__enclos_env__$private$test_content$wi$intruder
oolong_test$.__enclos_env__$private$test_content$wi$answer[1] <- "wronganswer"
```

@@

```{r, include = FALSE}
genius_topic <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$ti$answer <- obj1$.__enclos_env__$private$test_content$ti$intruder
    return(obj1)
}
genius_word <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$wi$answer <- obj1$.__enclos_env__$private$test_content$wi$intruder
    return(obj1)
}
oolong_test <- genius_word(genius_topic(oolong_test))
oolong_test$.__enclos_env__$private$test_content$ti$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$ti$candidates[[2]], 1)
oolong_test$lock()
```

@@

```{r warplda2}
### Just word intrusion test.
oolong_test <- wi(abstracts_warplda, userid = "Lionel")
oolong_test
```

@@

```{r, include = FALSE}
oolong_test$.__enclos_env__$private$test_content$gs <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
))
```

@@

```{r, include = FALSE}
trump$.__enclos_env__$private$test_content$gs <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))

trump2$.__enclos_env__$private$test_content$gs <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(5L, 3L, 2L, 5L, 3L, 1L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))
trump$lock()
trump2$lock()
```
